Linked Data Notifications: a resource-centric communication protocol

### 2017-03-22 index.tex
Mention the initial work on the Inbox in acknowledgements

\paragraph{Acknowledgements:}
This material is based on work supported by the Qatar Computing Research Institute (QCRI), and by the DFG project “Opening Scholarly Communication in Social Sciences” (grant agreement AU 340/9-1).

>>>>

\paragraph{Acknowledgements:}
The initial work on the Inbox was done by the Solid project. This material is based on work supported by the Qatar Computing Research Institute (QCRI), and by the DFG project “Opening Scholarly Communication in Social Sciences” (grant agreement AU 340/9-1).
